### 2015-04-09 rscripts/data_review.Rmd
re-arrange project, introduce arg parser

```{r, echo=FALSE}
src.dt <- fread("~/Dropbox/montreal/merged.o", header = F, sep=" ", colClasses = c("integer","integer","integer","integer"))
setnames(src.dt, c("user_id", "location_id", "login", "logout"))
setkey(src.dt, login, logout, user_id, location_id)
src.dt
```

@@

Trim data by:

1. sessions exceeding `r max_hours` hours
2. eliminate users that have fewer than `r min_logins` logins
3. eliminate locations that have fewer than `r min_logins` logins
4. recursively apply steps 2-3 until no users / locations eliminated

@@

@@

1. re-assign user ids from 1, ordered by first appearance
2. re-assign location ids from 1, ordered by first appearance
3. TODO split entries that cross days (~ 3% of data; of crossing entries, most look like late PM->early AM sessions, aka bar / club visits)
4. convert login / logout times to `log(in|out)_day` and `log(in|out)_time`

```{r, echo=FALSE}
censor.dt[,
  user_id := .GRP, by=user_id
][,
  location_id := .GRP, by=location_id
][,
  login_day := login %/% (24*60*60)
][,
  logout_day := logout %/% (24*60*60)
][,
  login_time := login - login_day*24*60*60
][,
  logout_time := logout - logout_day*24*60*60
]
setkey(censor.dt, login, logout, user_id, location_id)
save(censor.dt, file = "~/Dropbox/montreal/censored.Rdata")
# censor.dt[,list(
#   login_day = login %/% (24*60*60),
#   logout_day = logout %/% (24*60*60),
#   login_time = login %% (24*60*60)/(60*60),
#   logout_time = logout %% (24*60*60)/(60*60)
# ) ]
```

>>>>

```{r, echo=FALSE}
src.dt <- fread("../input/merged.o", header = F, sep=" ", colClasses = c("integer","integer","integer","integer"))
setnames(src.dt, c("user_id", "location_id", "login", "logout"))
setkey(src.dt, login, logout, user_id, location_id)
src.dt
```

@@

Trim data:

1. remove sessions exceeding `r max_hours` hours
2. eliminate users that have fewer than `r min_logins` logins
3. eliminate locations that have fewer than `r min_logins` logins
4. recursively apply steps 2-3 until no users / locations eliminated

@@

Removed `r dim(src.dt)[1] - dim(censor.dt)[1]` rows, or `r (dim(src.dt)[1] - dim(censor.dt)[1])/dim(src.dt)[1]` reduction.

@@

1. re-assign user ids from 1, ordered by first appearance
2. re-assign location ids from 1, ordered by first appearance
3. TODO split entries that cross days (~ 3% of data; of crossing entries, most look like late PM->early AM sessions, aka bar / club visits)
4. convert login / logout times to `log(in|out)_day` and `log(in|out)_time`
5. mark data as the empirical source: set `run_id = 0`, `sample_id = 0`, `target = FALSE`.

```{r, echo=FALSE}
censor.dt[,
  user_id := .GRP, by=user_id
][,
  location_id := .GRP, by=location_id
][,
  login_day := login %/% (24*60*60)
][,
  logout_day := logout %/% (24*60*60)
][,
  login_time := login - login_day*24*60*60
][,
  logout_time := logout - logout_day*24*60*60
][,
  run_id := 0
][,
  sample_id := 0
][,
  target := FALSE
]
setkey(censor.dt, run_id, sample_id, login_day, login_time, logout_day, logout_time, user_id, location_id)
save(censor.dt, file = "../input/censored.Rdata")
```
